Intro to Data

### 2018-08-31 DATA606/Intro to Data.Rmd
Additional work

@@

@@

@@

@@

@@

@@

>>>>

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_50.png)

**(a) is a normal distribution.  The corresponding box plot is 2**

**(b) is a uniform distribution.  3 is the box plot**

**(c) is a long-tailed or right skewed distribution and 1 is the box plot**

@@

**This is long tailed right skewed distribution.  The median would be the best option to represent the central tendancy and IQR would be best for the spread.  Since "the are a meaningful number" of very expensive houses, the mean would be larger than the median and less representative of the average.**

@@

**This is symetric distribution.  Mean and standard deviation could be used on this distribution because the spread is much more compact than the previous example.**

@@

**This is a bimodal distribution.  You can't use median or mean to summarize because it really isn't meaningful.**

@@

**This is probably a symetric distribution with some outliers on the right tail.  A median and IQR would be the best choice because of the top level executives would pull the mean to the right.**

@@

![ ](https://github.com/mikeasilva/CUNY-SPS/raw/master/DATA606/intro_to_data_1_70.png)

@@

**Survival is dependent of whether the patient got a transplant.  The probability (proportion) of living when they got the treatment is larger than that when they did not.**
